---
title: "Integrating Pearson Correlations"
author: "LNguyen"
date: "12/11/2024"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).


#LIZZY INTEGRATION FROM HERE DOWN
```{r}
#load em up bois
library(shiny)
library(leaflet)
library(geojsonio)
library(tidyverse)
library(sf)
library(ggrepel)
library(plotly)

#prepare the data sets?
#I NEED TO FIX THESE MANUALLY TO PICK OUT THE RIGHT COLUMNS

#obesity??
unfiltered_obesity_df <- read_csv("obese_overweight_adults.csv")
filtered_obesity_df <- unfiltered_obesity_df %>%
  select(1, 2, 3, 4) %>%
  filter(unfiltered_obesity_df$year == 2016)


#happiness??
unfiltered_happy_df <- read_csv("happiness_index_tidy.csv") 
filtered_happy_df <- unfiltered_happy_df %>%
  select(2, 3, 11) %>%
  filter(unfiltered_happy_df$year == 2016)

#gdp??
unfiltered_gdp_df <- read_csv("GDP_tidy.csv")
filtered_gdp_df <- unfiltered_gdp_df %>%
  select(2, 4, 5, 6) %>%
  filter(unfiltered_gdp_df$year == 2016)

#table joins
country_pop <- read_csv("country_pop.csv") 

country_pop <- country_pop %>%
  select(2, "2016")

colnames(country_pop)[colnames(country_pop) == "Country Code"] <- "Code"

colnames(country_pop)[colnames(country_pop) == "2016"] <- "Population"

result <-  filtered_obesity_df %>%
  left_join(filtered_happy_df, by = "country")
variables_df <- result %>%
  left_join(filtered_gdp_df, by = "country")

variables_df <- variables_df %>%
  select(1, 2, 3, 4, 6, 8, 9) 

write.csv(variables_df, "~/Shepherd/variables_df.csv", row.names = FALSE)



#ordering eggs server side up
  
server <- function(input, output) {
  
  print(colnames(variables_df))  #okay did it give me the columns i wanted or not

    # Join with population data (assuming 'country_pop' has 'Code' and 'Population')
  variables_df <- variables_df %>%
    left_join(country_pop, by = c("code.x" = "Code"))

  # Check if Population column is added
  print(colnames(variables_df))
  
  
  #Get rid of NA gdp rows, then create a column with calculated gdp_per_capita
  clean_variables_df <- variables_df %>%
    filter(!is.na(gdp) & !is.na(Population)) %>%  # Use 'variables_df' instead of 'filtered_variables_df'
    mutate(gdp_per_capita = (gdp / Population))
  
  #Correlation time
  
  #CORRELATION BETWEEN OBESITY AND GDP PER CAPITA
  correlation_1 <- cor(clean_variables_df$gdp_per_capita, clean_variables_df$percentBMI30, method = "pearson", use = "complete.obs")
  
  #Render plot (obesity, gdp per capita)
  output$Obesity_GDPpercapita_plot <- renderPlot({
    ggplot(clean_variables_df, aes(x = gdp_per_capita, y = percentBMI30)) +
     geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
      geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
      geom_text_repel(aes(label = country), size = 3) +  # Add non-overlapping country labels
      labs(
        title = "GDP per Capita vs Obesity Rate",
        subtitle = paste("Pearson Correlation: ", round(correlation_1, 2)),
        x = "GDP per Capita",
        y = "Obesity Rate"
      ) +
      theme_minimal()
    
  })
  
  #CORRELATION BETWEEN OBESITY AND GROSS GDP
  correlation_2 <- cor(clean_variables_df$gdp, clean_variables_df$percentBMI30, method = "pearson", use = "complete.obs")
  output$Obesity_GDPgross_plot <- renderPlot({
    ggplot(clean_variables_df, aes(x = gdp, y = percentBMI30)) +
  geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
  geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
  geom_text_repel(aes(label = country), size = 3) +  # Add non-overlapping country labels
  labs(
    title = "GDP vs Obesity Rate",
    subtitle = paste("Pearson Correlation: ", round(correlation_2, 2)),
    x = "GDP",
    y = "Obesity Rate"
  ) +
  theme_minimal()
  })
  
  
}

#UI TIME BABYYYY
#SWAP OUT CODE TO DO HAPPINESS_GDP GROSS IF YOU WANT
ui <- fluidPage(
  titlePanel("Pearson Correlations"),
  
  plotOutput("Obesity_GDPpercapita_plot"),
  plotOutput("Obesity_GDPgross_plot"),
  
  plotOutput("Happiness_GDPpercapita_plot"),
  
  #plotOutput("Happiness_GDPgross_plot") #if I want to I can put this in here
  
  plotOutput("Obesity_Happiness_plot")
)

  
shinyApp(ui = ui, server = server)
```






# Obesity and GDP per Capita

```{r}

#HOW DO I DO THIS BEFORE THE VISUALIZATION
filtered_variables_df <- filtered_variables_df %>% 
  filter(!is.na(gdp))

# GDP_min <- min(filtered_variables_df$gdp, na.rm = TRUE)
# GDP_max <- max(filtered_variables_df$gdp, na.rm = TRUE)

# Now proceed with any further operations
clean_variables_df <- filtered_variables_df %>%
  mutate(gdp_per_capita = (gdp / Population))

# Calculate Pearson correlation
correlation <- cor(clean_variables_df$gdp_per_capita, clean_variables_df$percentBMI30, method = "pearson", use = "complete.obs")

plot <- ggplot(clean_variables_df, aes(x = gdp_per_capita, y = percentBMI30)) +
  geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
  geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
  geom_text_repel(aes(label = country), size = 3) +  # Add non-overlapping country labels
  labs(
    title = "GDP per Capita vs Obesity Rate",
    subtitle = paste("Pearson Correlation: ", round(correlation, 2)),
    x = "GDP per Capita",
    y = "Obesity Rate"
  ) +
  theme_minimal()

# Print the plot
print(plot)
```


#HAVE NOT DONE ANY OF THESE YET. WILL INTEGRATE ONCE THE FIRST ONE WORKS

# Obesity and GDP 

```{r}
correlation <- cor(clean_variables_df$gdp, clean_variables_df$percentBMI30, method = "pearson", use = "complete.obs")

plot <- ggplot(clean_variables_df, aes(x = gdp, y = percentBMI30)) +
  geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
  geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
  geom_text_repel(aes(label = country), size = 3) +  # Add non-overlapping country labels
  labs(
    title = "GDP vs Obesity Rate",
    subtitle = paste("Pearson Correlation: ", round(correlation, 2)),
    x = "GDP",
    y = "Obesity Rate"
  ) +
  theme_minimal()

# Print the plot
print(plot)
```

# GDP per Capita and Happiness
```{r}
#Calculate Pearson correlation

correlation2 <- cor(clean_variables_df$gdp_per_capita, clean_variables_df$positive_affect, method = "pearson", use = "complete.obs")

plot <- ggplot(clean_variables_df, aes(x = gdp_per_capita, y = positive_affect)) +
  geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
  geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
  geom_text_repel(aes(label = country), size = 3) +  # Add non-overlapping country labels
  labs(
    title = "GDP per Capita vs Happiness Level",
    subtitle = paste("Pearson Correlation: ", round(correlation2, 2)),
    x = "GDP per Capita",
    y = "Happiness Level"
  ) +
  theme_minimal()

# Print the plot
print(plot)
```




# GDP per Capita and Happiness
```{r}
#Calculate Pearson correlation

correlation2 <- cor(clean_variables_df$gdp_per_capita, clean_variables_df$positive_affect, method = "pearson", use = "complete.obs")

plot <- ggplot(clean_variables_df, aes(x = gdp_per_capita, y = positive_affect)) +
  geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
  geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
  geom_text_repel(aes(label = country), size = 3) +  # Add non-overlapping country labels
  labs(
    title = "GDP per Capita vs Happiness Level",
    subtitle = paste("Pearson Correlation: ", round(correlation2, 2)),
    x = "GDP per Capita",
    y = "Happiness Level"
  ) +
  theme_minimal()

# Print the plot
print(plot)
```

# Obesity and Happiness

```{r}
#Calculate Pearson correlation

correlation3 <- cor(clean_variables_df$percentBMI30, clean_variables_df$positive_affect, method = "pearson", use = "complete.obs")

plot <- ggplot(clean_variables_df, aes(x = percentBMI30, y = positive_affect)) +
  geom_point(color = "blue", alpha = 0.7) +  # Scatter plot
  geom_smooth(method = "lm", color = "red", se = TRUE) +  # Line of best fit
  geom_text_repel(aes(label = country), 
                   size = 3, 
                   max.overlaps = 100) +  # Increase max.overlaps
  labs(
    title = "Obesity Rate vs Happiness Level",
    subtitle = paste("Pearson Correlation: ", round(correlation3, 2)),
    x = "Obesity Rate",
    y = "Happiness Level"
  ) +
  theme_minimal()

# Print the plot
print(plot)
```