---
title: "shiny_app.rmd"
author: "Brian"
date: "11/11/2024"
output: html_document

---

<<<<<<< HEAD
#Packages used
```{r}
library(shiny)
library(tidyverse)
library(dplyr)
library(leaflet)
library(readr)
library(geojsonio)


```

#11/11/24 - Lizzy Nguyen
#Produced all Domino's data, Brian uploaded them
  #Domestic Domino's Locations Finalized.csv
  #International Domino's Locations (Finalized).csv

#Created both the ui.r and server.r servers
#Added 3 navigation panels in ui.r named "Longitudinal Chloropleths", "Correlational Matrix", and "Fast Food Mania"

#In "Longitudinal Chloropleths", created a (currently unattached) widget with 
  #a year slider (1975-2016)
  #4-button choice panel with each global factor (Adult Obesity, Gross GDP, Gini Inequality, Happiness Index)
  
=======
# loading shiny package

```{r}
#opening relevant files

obese_overweight_adults <- read_csv("obese_overweight_adults.csv")

GDP_tidy <- read_csv("GDP_tidy.csv")

Gini_Inequality_Index_tidy <- read_csv("Gini_Inequality_Index_tidy.csv")


happiness_index_tidy <- read_csv("happiness_index_tidy.csv")

countries.geo.json <- read_csv("countries.geo.json")

```

>>>>>>> e6bd5ba37398a910fd941f9dfae25f033275e168



